Spatio-angular fluorescence microscopy I. Basic theory (Draft: \today)

### 2018-11-24 papers/basic-theory/paper/paper.tex
First few edits from Patrick.

\author{Talon Chandler,\authormark{1,*} Authors TBD,\authormark{2,*}Hari Shroff\authormark{2,*}, Rudolf Oldenbourg\authormark{2,*}, and Patrick La Rivi\`ere \authormark{1}}

@@

\begin{abstract*}
  We introduce the basic elements of a spatio-angular theory of fluorescence
  microscopy. We start by modeling an aplanatic microscope imaging an ensemble
  of in-focus fluorescent dipoles as a linear Hilbert-space operator with domain
  $\mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$ and range $\mbb{L}_2(\mbb{R}^2)$, and we
  express the operator in terms of four different sets of object-space basis
  functions. We show that the operator takes a particularly convenient form when
  expressed in a basis of spatial and spherical harmonics---a form we call the
  dipole spatio-angular transfer function. We demonstrate our formalism by
  analyzing a single-view fluorescence microscope without using the monopole or
  scalar approximations. We show that this imaging system has an angular band
  limit, and we demonstrate the value of the transfer function approach by
  efficiently simulating the imaging process with simple phantoms. Notably, we
  show that information about the out-of-plane orientation of ensembles of
  in-focus fluorophores is recorded by fluorescence microscopes. We discuss the
  implications of our analysis for all quantitative fluorescence microscopy
  studies and lay out a path towards a complete theory.
\end{abstract*}

>>>>

\author{Talon Chandler,\authormark{1,*} Authors TBD,\authormark{2,*}, Rudolf Oldenbourg\authormark{2,*}, and Patrick La Rivi\`ere \authormark{1}}

@@

\begin{abstract*}
  We introduce the basic elements of a spatio-angular theory of fluorescence
  microscopy. We start by modeling an aplanatic microscope imaging an ensemble
  of in-focus fluorescent dipoles as a linear Hilbert-space
  operator, % with domain
  % $\mbb{L}_2(\mbb{R}^2\times\mbb{S}^2)$ and range $\mbb{L}_2(\mbb{R}^2)$
  and we express the operator in terms of four different sets of object-space
  basis functions. We show that the operator takes a particularly convenient
  form when expressed in a basis of spatial and spherical harmonics---a form we
  call the dipole spatio-angular transfer function. We demonstrate our formalism
  by analyzing a single-view fluorescence microscope without using the monopole
  or scalar approximations. We show that this imaging system has an angular band
  limit, and we demonstrate the value of the transfer function approach by
  efficiently simulating the imaging process with simple phantoms. Notably, we
  show that information about the out-of-plane orientation of ensembles of
  in-focus fluorophores is recorded by fluorescence microscopes. We discuss the
  implications of our analysis for all quantitative fluorescence microscopy
  studies and lay out a path towards a complete theory.
\end{abstract*}
